
# Import library
```{r}
#getwd()
library(lubridate)
library(zoo)
library(quantmod)
library(fBasics)
library(tseries)
library(sandwich)
library(lmtest)
library(lattice)
library(xtable)
library(vars)
library(plyr)
library(dplyr)
library(gridExtra)
library(corrplot)
library(ggplot2)
library(reshape2)
library(data.table)
library(rvest)
library(plm)
library(stringr)
library(tidyverse)
library(foreign)
library(stargazer)

```

### Read Final_Data_Country
```{r}
datweekly_panel<-read.csv("./Data/Final_Data_Country.csv",header=T,sep=',')
# Remove lagged variables
datweekly_panel<-datweekly_panel %>% select(-contains("Lagged"))
datweekly_panel$latitude <- NULL
datweekly_panel$longitude <- NULL
```

### Alternative SI measures
```{r}
weight <- 1/7*(1/4 + 1/4 + 1/3 + 1/5 + 1/3 + 1/4 + 1/3)

### create sub-indices
datweekly_panel$C1_sub <- 100*(datweekly_panel$C1_School.closing*(1-weight)/3 + weight*datweekly_panel$C1_Flag)
datweekly_panel$C2_sub <- 100*(datweekly_panel$C2_Workplace.closing*(1-weight)/3 + weight*datweekly_panel$C2_Flag)
datweekly_panel$C3_sub <- 100*(datweekly_panel$C3_Cancel.public.events*(1-weight)/2 + weight*datweekly_panel$C3_Flag)
datweekly_panel$C4_sub <- 100*(datweekly_panel$C4_Restrictions.on.gatherings*(1-weight)/4 + weight*datweekly_panel$C4_Flag)
datweekly_panel$C5_sub <- 100*(datweekly_panel$C5_Close.public.transport*(1-weight)/2 + weight*datweekly_panel$C5_Flag)
datweekly_panel$C6_sub <- 100*(datweekly_panel$C6_Stay.at.home.requirements*(1-weight)/3 + weight*datweekly_panel$C6_Flag)
datweekly_panel$C7_sub <- 100*(datweekly_panel$C7_Restrictions.on.internal.movement*(1-weight)/2 + weight*datweekly_panel$C7_Flag)
datweekly_panel$C8_sub <- 100*(datweekly_panel$C8_International.travel.controls/4)

### count NA 
datweekly_panel$count_na <- sum(is.na(datweekly_panel$C1_School.closing) + 
                                   is.na(datweekly_panel$C2_School.closing) + 
                                   is.na(datweekly_panel$C3_School.closing) +
                                   is.na(datweekly_panel$C4_School.closing) +
                                   is.na(datweekly_panel$C5_School.closing) +
                                   is.na(datweekly_panel$C6_School.closing) +
                                   is.na(datweekly_panel$C7_School.closing) +
                                   is.na(datweekly_panel$C8_School.closing))

datweekly_panel$count_na_v1 <- sum(is.na(datweekly_panel$C1_School.closing) + 
                                   is.na(datweekly_panel$C2_School.closing) + 
                                   is.na(datweekly_panel$C3_School.closing) +
                                   is.na(datweekly_panel$C4_School.closing) +
                                   is.na(datweekly_panel$C5_School.closing) +
                                   is.na(datweekly_panel$C6_School.closing) +
                                   is.na(datweekly_panel$C7_School.closing))

### replace NA with zero
datweekly_panel$C1_sub[which(is.na(datweekly_panel$C1_sub))] <- 0
datweekly_panel$C2_sub[which(is.na(datweekly_panel$C2_sub))] <- 0
datweekly_panel$C3_sub[which(is.na(datweekly_panel$C3_sub))] <- 0
datweekly_panel$C4_sub[which(is.na(datweekly_panel$C4_sub))] <- 0
datweekly_panel$C5_sub[which(is.na(datweekly_panel$C5_sub))] <- 0
datweekly_panel$C6_sub[which(is.na(datweekly_panel$C6_sub))] <- 0
datweekly_panel$C7_sub[which(is.na(datweekly_panel$C7_sub))] <- 0
datweekly_panel$C8_sub[which(is.na(datweekly_panel$C8_sub))] <- 0

### create alternative SI measures

datweekly_panel$SI_alt1 <- 1/8*(datweekly_panel$C1_sub + datweekly_panel$C2_sub + datweekly_panel$C3_sub + datweekly_panel$C4_sub + 
                                   datweekly_panel$C5_sub + datweekly_panel$C6_sub + datweekly_panel$C7_sub + datweekly_panel$C8_sub)
datweekly_panel$SI_alt1[which(datweekly_panel$count_na >= 3)] <- NA

datweekly_panel$SI_alt2 <- 1/7*(datweekly_panel$C1_sub + datweekly_panel$C2_sub + datweekly_panel$C3_sub + datweekly_panel$C4_sub + 
                                   datweekly_panel$C5_sub + datweekly_panel$C6_sub + datweekly_panel$C7_sub)
datweekly_panel$SI_alt2[which(datweekly_panel$count_na_v1 >= 2)] <- NA

```


### Merge global preference survey data to Final_Data_Country
```{r}
gps.country <- read.dta("./Data/GPS_dataset_country_level/country_v11.dta")
# Change country names for merge
gps.country[which(gps.country$country == "South Korea"),"country"] <- "Korea, South"
gps.country[which(gps.country$country == "Czech Republic"),"country"] <- "Czechia"
gps.country[which(gps.country$country == "United States"),"country"] <- "US"

gps.individual <- read.dta("./Data/GPS_dataset_individual_level/individual_v11_new.dta")
# Change country names for merge
gps.individual[which(gps.individual$country == "South Korea"),"country"] <- "Korea, South"
gps.individual[which(gps.individual$country == "Czech Republic"),"country"] <- "Czechia"
gps.individual[which(gps.individual$country == "United States"),"country"] <- "US"

gps.individual$age <- as.character(gps.individual$age)
gps.individual[which(gps.individual$age == "99 99+"), "age"] <- "99"
gps.individual[which(gps.individual$age == "100 (Refused"), "age"] <- NA
gps.individual$age <- as.numeric(gps.individual$age)
gps.individual.pop65 <- gps.individual[which(!is.na(gps.individual$age) & gps.individual$age > 65), ]
gps.individual.pop65 <- gps.individual.pop65[which(!is.na(gps.individual.pop65$trust)),]
gps.country.pop65 <- ddply(gps.individual.pop65, "country", function(X) data.frame(wm.trust = weighted.mean(X$trust, X$wgt)))

colnames(gps.country)[1] <- "COUNTRY"
datweekly_panel <- merge(datweekly_panel, gps.country, by=c("COUNTRY"), all.x=TRUE)
colnames(gps.country.pop65)[1] <- "COUNTRY"
datweekly_panel <- merge(datweekly_panel, gps.country.pop65, by=c("COUNTRY"), all.x=TRUE)
```

### Rename variables and create some new variables
```{r}
datweekly_panel<-pdata.frame(datweekly_panel, index = c("COUNTRY", "Date"))
datweekly_panel$Date<-as.Date(datweekly_panel$Date,"%Y-%m-%d")
#reorder
datweekly_panel<-datweekly_panel[order(datweekly_panel$Date),]
datweekly_panel<-datweekly_panel[order(datweekly_panel$COUNTRY),]

colnames(datweekly_panel)[colnames(datweekly_panel) == "Total_Cases_Country"] <- "Total_Case_Country"
colnames(datweekly_panel)[colnames(datweekly_panel) == "Total_Deceased_Country"] <- "Total_Death_Country"
colnames(datweekly_panel)[colnames(datweekly_panel) == "New_Confirmed_Country"] <- "New_Case_Country"
colnames(datweekly_panel)[colnames(datweekly_panel) == "New_Total_Deceased_Country"] <- "New_Death_Country"
colnames(datweekly_panel)[colnames(datweekly_panel) == "Total_Mortality_Rate_Per_Capita"] <- "Total_Mortality_Rate"
colnames(datweekly_panel)[colnames(datweekly_panel) == "New_Mortality_Rate_Per_Capita"] <- "New_Mortality_Rate"
colnames(datweekly_panel)[colnames(datweekly_panel) == "Total_Cases_Country_Per_Capita"] <- "Total_Case_Rate"
colnames(datweekly_panel)[colnames(datweekly_panel) == "rolling_average_confirmed"] <- "RollingAverage_New_Case_Country"
colnames(datweekly_panel)[colnames(datweekly_panel) == "rolling_average_deceased"] <- "RollingAverage_New_Death_Country"
colnames(datweekly_panel)[colnames(datweekly_panel) == "total_rolling_average_mortality"] <- "RollingAverage_Total_Mortality_Rate"
colnames(datweekly_panel)[colnames(datweekly_panel) == "new_rolling_average_mortality"] <- "RollingAverage_New_Mortality_Rate"
colnames(datweekly_panel)[colnames(datweekly_panel) == "EUI_democracy"] <- "EIU_Democracy"
datweekly_panel$RollingAverage_Total_Mortality_Rate <- NULL
datweekly_panel$longitude <- NULL

datweekly_panel$New_Case_Rate = datweekly_panel$New_Case_Country/datweekly_panel$Population

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(RollingAverage_New_Case_Rate = frollmean(New_Case_Rate, 7,na.rm=TRUE))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(Total_Mortality_Rate_Growth = log(Total_Mortality_Rate) - Lag(log(Total_Mortality_Rate),7))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(Total_Case_Rate_Growth = log(Total_Case_Rate) - Lag(log(Total_Case_Rate),7))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Case_Rate_Growth = log(RollingAverage_New_Case_Rate) - Lag(log(RollingAverage_New_Case_Rate),7))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth = log(RollingAverage_New_Mortality_Rate) - Lag(log(RollingAverage_New_Mortality_Rate),7))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth_lag1 = dplyr::lag(New_Mortality_Rate_Growth,1))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth_lead7 = dplyr::lead(New_Mortality_Rate_Growth,7))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth_lead14 = dplyr::lead(New_Mortality_Rate_Growth,14))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth_lead21 = dplyr::lead(New_Mortality_Rate_Growth,21))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth_lead28 = dplyr::lead(New_Mortality_Rate_Growth,28))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth_lead35 = dplyr::lead(New_Mortality_Rate_Growth,35))

datweekly_panel <- datweekly_panel %>%
  group_by(COUNTRY) %>%
  mutate(StringencyIndex_Change = StringencyIndex - Lag(StringencyIndex, 7))

datweekly_panel$respiratory_deaths_rate <- 1/3*(datweekly_panel$respiratory_deaths/datweekly_panel$Population)
```

### First Half Dummy
```{r}
datweekly_panel$First_Half <- 0
datweekly_panel$Days <- NA

for (country in unique(datweekly_panel$COUNTRY)){
   
   first_date_new_mortality_growth_rate <- min(datweekly_panel$Date[which(datweekly_panel$COUNTRY == country & 
                                                                             !is.na(datweekly_panel$New_Mortality_Rate_Growth) &
                                                                             !is.infinite(datweekly_panel$New_Mortality_Rate_Growth))])
   last_date <- as.Date("2020-04-28")
   datweekly_panel$First_Half[which(datweekly_panel$COUNTRY == country & datweekly_panel$Date < (floor((last_date - first_date_new_mortality_growth_rate)/2) + first_date_new_mortality_growth_rate))] <- 1
   datweekly_panel$Days[which(datweekly_panel$COUNTRY == country & datweekly_panel$Date >= first_date_new_mortality_growth_rate)] <- datweekly_panel$Date[which(datweekly_panel$COUNTRY == country & datweekly_panel$Date >= first_date_new_mortality_growth_rate)] - first_date_new_mortality_growth_rate
}
```

### Reorder columns
```{r}
datweekly_panel <- datweekly_panel %>%
 select(c("COUNTRY", "X", "Date",
          "Total_Case_Country", "Total_Death_Country", "New_Case_Country", "New_Death_Country", "Population",
          "Total_Case_Rate", "Total_Mortality_Rate", "New_Case_Rate", "New_Mortality_Rate", 
          "RollingAverage_New_Case_Country", "RollingAverage_New_Death_Country", 
          "RollingAverage_New_Case_Rate", "RollingAverage_New_Mortality_Rate", 
          "Total_Case_Rate_Growth", "Total_Mortality_Rate_Growth", 
          "New_Case_Rate_Growth", "New_Mortality_Rate_Growth"), everything())

datweekly_panel$Total_Case_Rate_Growth[is.nan(datweekly_panel$Total_Case_Rate_Growth)] <- NA
datweekly_panel$Total_Mortality_Rate_Growth[is.nan(datweekly_panel$Total_Mortality_Rate_Growth)] <- NA

datweekly_panel$New_Case_Rate_Growth[is.nan(datweekly_panel$New_Case_Rate_Growth)] <- NA
datweekly_panel$New_Mortality_Rate_Growth[is.nan(datweekly_panel$New_Mortality_Rate_Growth)] <- NA

datweekly_panel$New_Mortality_Rate_Growth[is.infinite(-datweekly_panel$New_Mortality_Rate_Growth)] <- Inf

colnames(datweekly_panel)
```

### Baseline regressions - benchmark
```{r}

# datweekly_panel <- datweekly_panel[which(datweekly_panel$StringencyIndex > 67),]

regmod <- list()
se_t_stats <- list()
se <- list()

###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
for (day_lead in seq(14,28,7)){
   datweekly_panel <- datweekly_panel %>%
      group_by(COUNTRY) %>%
      mutate(New_Mortality_Rate_Growth_lead_temp = dplyr::lead(New_Mortality_Rate_Growth,day_lead))
   
   datweekly_panel <- datweekly_panel %>% ungroup()
   datweekly_panel <- pdata.frame(datweekly_panel, index = c("COUNTRY", "Date"))
   datweekly_panel <- datweekly_panel[order(datweekly_panel$Date),]
   datweekly_panel <- datweekly_panel[order(datweekly_panel$COUNTRY),]
   
   regmod[[day_lead/7-1]] <- plm(lead(New_Mortality_Rate_Growth,day_lead)~StringencyIndex+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead_temp)),],na.action="na.exclude")
   se[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))
   se_t_stats[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))[,2]
   
}
```

### HTML output of baseline regression results
```{r,warning=FALSE, results='hide',message=FALSE}
stargazer(digits=6,regmod,type="html",se=se_t_stats,out=file.path("Outputs_revision","Table_baseline_panel_output_benchmark.htm"),
          column.labels=c("Weekly New Mortality Growth (t+14)", "Weekly New Mortality Growth (t+21)", "Weekly New Mortality Growth (t+28)"),
          dep.var.labels.include = FALSE,
          covariate.labels=c("Stringency (t)","New Mortality Growth (t-1)"), df = FALSE,omit.stat="adj.rsq",notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",title="Local Projection Regressions",add.lines = list(c("Fixed effects?", "Y","Y","Y")))
```

### Plots
```{r}
### plot of 10-unit increase in Stringency effects over time on future mortality growth
p.dat_weekly<-c(coef(regmod[[1]])[1],coef(regmod[[2]])[1],coef(regmod[[3]])[1])
p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly+1.96*c(se[[1]][1,2],se[[2]][1,2],se[[3]][1,2]))
p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly[,1]-1.96*c(se[[1]][1,2],se[[2]][1,2],se[[3]][1,2]))
colnames(p.dat_weekly)<-c("mean","upper","lower")
p.dat_weekly<-data.frame(p.dat_weekly)*10*100
                                                                                   
p0<-ggplot(data=p.dat_weekly,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean))+geom_point(size=4,shape=21,fill="grey")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+geom_errorbar(aes(ymin=lower,ymax=upper))+ggtitle("Average Impact")

ggsave(file.path("Outputs_revision","Figure_baseline_panel_benchmark.png"), width = 5, height = 5)
                                                                                                                
p0
```

### Loop to generate heterogeneity regression results
```{r}
###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
var.list <- c("prop65", "propurban", "Latitude", "Longitude", "popdensity", "arrivals", "departures", "vul_emp", "GNI", "health_exp", "pollution", "EIU_Democracy", "trust", "risktaking")
label.list <- c("Proportion 65+", "Proportion Urban", "Latitude", "Longitude", "Population Density", "Log(Arrivals)", "Log(Departures)", "Vulnerable Employees", "Log(GNI per capita)", "Health Expenditures", "Pollution", "EIU Democracy", "Trust", "Risk Taking")

p.dat_weekly.list <- list()
s.list <- list()

for (i in c(1:length(var.list))){

   var <- var.list[i]
   label <- label.list[i]
   
   if (var == "arrivals" || var == "departures" || var == "GNI"){
      regmoda<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead14~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")")),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
      se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
      regmodb<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead21~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")")),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
      se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
      regmodc<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead28~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")")),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
      se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
   }else{
   regmoda<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead14~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:",var)),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
   se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
   regmodb<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead21~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:",var)),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
   se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
   regmodc<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead28~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:",var)),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
   se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
   }
   
   stargazer(digits=6,regmoda,regmodb,regmodc,type="html",
             se=list(se.a[,2],se.b[,2],se.c[,2]),out=paste("Table_panel_",var,"_weekly_reg_output_benchmark.htm", sep = ""),
             dep.var.labels.include = FALSE,
             column.labels=c("Weekly New Mortality Growth (t+14)", "Weekly New Mortality Growth (t+21)", "Weekly New Mortality Growth (t+28)", "Weekly New Mortality Growth (t+35)"),
             covariate.labels=c("Stringency (t)","New Mortality Growth (t-1)",paste("Stringency (t) X ", label)), 
             df = FALSE,omit.stat="adj.rsq",
             notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",
             title=paste("Heterogeneity: ", label),add.lines = list(c("Fixed effects?", "Y","Y","Y")))
   
   ### plot of 10-unit increase in Stringency effects over time on future mortality growth
   p.dat<-c(coef(regmoda)[1],coef(regmodb)[1],coef(regmodc)[1])
   i.dat<-c(coef(regmoda)[3],coef(regmodb)[3],coef(regmodc)[3])
   effect.dat<-cbind(p.dat, i.dat)
   #p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly+1.96*c(se.a[2,2],se.b[2,2],se.c[2,2],se.d[2,2]))
   #p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly[,1]-1.96*c(se.a[2,2],se.b[2,2],se.c[2,2],se.d[2,2]))
   colnames(effect.dat)<-c("mean.1", "mean.2")
   
   p.dat_weekly.list[[i]]<-data.frame(effect.dat)*10*100
   
   ###figure out the 25% percentile  and 75% percentile of elderly population rate across countries, to compare effects of a 10-unit rise in stringency level
   if (var == "arrivals" || var == "departures" || var == "GNI"){
      
   s.list[[i]] <- summary(unique(log(datweekly_panel[[var]])))
   }else{
      s.list[[i]] <- summary(unique(datweekly_panel[[var]]))
   }
   s.list
}

```

### Loop to generate heterogeneity regression results
```{r, eval = FALSE}
###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
var.list <- c("prop65", "propurban", "Latitude", "Longitude", "popdensity", "arrivals", "departures", "vul_emp", "GNI", "health_exp", "pollution", "EIU_Democracy", "trust", "risktaking")
label.list <- c("Proportion 65+", "Proportion Urban", "Latitude", "Longitude", "Population Density", "Log(Arrivals)", "Log(Departures)", "Vulnerable Employees", "Log(GNI per capita)", "Health Expenditures", "Pollution", "EIU Democracy", "Trust", "Risk Taking")

p.dat_weekly.list <- list()
s.list <- list()

for (i in c(1:length(var.list))){

   var <- var.list[i]
   label <- label.list[i]
   
   if (var == "arrivals" || var == "departures" || var == "GNI"){
      regmoda<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead14~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")","+New_Mortality_Rate_Growth_lag1:","log(",var,")")),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
      se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
      regmodb<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead21~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")","+New_Mortality_Rate_Growth_lag1:","log(",var,")")),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
      se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
      regmodc<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead28~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")","+New_Mortality_Rate_Growth_lag1:","log(",var,")")),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
      se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
   }else{
   regmoda<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead14~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:",var,"+New_Mortality_Rate_Growth_lag1:",var)),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
   se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
   regmodb<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead21~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:",var,"+New_Mortality_Rate_Growth_lag1:",var)),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
   se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
   regmodc<-plm(as.formula(paste("New_Mortality_Rate_Growth_lead28~StringencyIndex","+New_Mortality_Rate_Growth_lag1","+StringencyIndex:",var,"+New_Mortality_Rate_Growth_lag1:",var)),method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
   se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
   }
   
   stargazer(digits=6,regmoda,regmodb,regmodc,type="html",
             se=list(se.a[,2],se.b[,2],se.c[,2]),out=paste("Table_panel_",var,"_weekly_reg_output_benchmark.htm", sep = ""),
             dep.var.labels.include = FALSE,
             column.labels=c("Weekly New Mortality Growth (t+14)", "Weekly New Mortality Growth (t+21)", "Weekly New Mortality Growth (t+28)", "Weekly New Mortality Growth (t+35)"),
             covariate.labels=c("Stringency (t)","New Mortality Growth (t-1)",paste("Stringency (t) X ", label),paste("New Mortality Growth (t-1)", label)), 
             df = FALSE,omit.stat="adj.rsq",
             notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",
             title=paste("Heterogeneity: ", label),add.lines = list(c("Fixed effects?", "Y","Y","Y")))
   
   ### plot of 10-unit increase in Stringency effects over time on future mortality growth
   p.dat<-c(coef(regmoda)[1],coef(regmodb)[1],coef(regmodc)[1])
   i.dat<-c(coef(regmoda)[2],coef(regmodb)[2],coef(regmodc)[2])
   effect.dat<-cbind(p.dat, i.dat)
   #p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly+1.96*c(se.a[2,2],se.b[2,2],se.c[2,2],se.d[2,2]))
   #p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly[,1]-1.96*c(se.a[2,2],se.b[2,2],se.c[2,2],se.d[2,2]))
   colnames(effect.dat)<-c("mean.1", "mean.2")
   
   p.dat_weekly.list[[i]]<-data.frame(effect.dat)*10*100
   
   ###figure out the 25% percentile  and 75% percentile of elderly population rate across countries, to compare effects of a 10-unit rise in stringency level
   if (var == "arrivals" || var == "departures" || var == "GNI"){
      
   s.list[[i]] <- summary(unique(log(datweekly_panel[[var]])))
   }else{
      s.list[[i]] <- summary(unique(datweekly_panel[[var]]))
   }
   s.list
}

```

### Plot Proportion 65+
```{r}
   #plot
   p1 <- ggplot(data=p.dat_weekly.list[[1]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*19.400))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*19.400),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+geom_point(size=4,aes(y=mean.1+mean.2*8.283),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*8.283)),linetype=2)+ggtitle(label.list[1])+ylim(-27,10)
   p1
```

### Plot Proportion Urban
```{r}
   #plot
   p2 <- ggplot(data=p.dat_weekly.list[[2]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*86.56))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*86.56),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*66.47),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*66.47)),linetype=2)+ggtitle(label.list[2])+ylim(-27,10)
   p2
```

### Plot Latitude
```{r}
   #plot
   p3 <- ggplot(data=p.dat_weekly.list[[3]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*50.83))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*50.83),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*22.01),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*22.01)),linetype=2)+ggtitle(label.list[3])+ylim(-27,10)
   p3
   
```

### Plot Longitude
```{r}
   #plot
   p4 <- ggplot(data=p.dat_weekly.list[[4]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*49.333))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*49.333),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*3.342),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*3.342)),linetype=2)+ggtitle(label.list[4])+ylim(-27,10)
   p4
```

### Plot Population Density
```{r}
   #plot
   p5 <- ggplot(data=p.dat_weekly.list[[5]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*223.847))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*223.847),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*33.375),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*33.375)),linetype=2)+ggtitle(label.list[5])+ylim(-27,10)
   p5
```

### Plot Log Arrivals
```{r}
   #plot
   p6 <- ggplot(data=p.dat_weekly.list[[6]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.94))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.94),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*15.30),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*15.30)),linetype=2)+ggtitle(label.list[6])+ylim(-27,10)
   p6
```

### Plot Log Departures
```{r}
   #plot
   p7 <- ggplot(data=p.dat_weekly.list[[7]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.79))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.79),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*15.02),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*15.02)),linetype=2)+ggtitle(label.list[7])+ylim(-27,10)
   p7
```

### Plot Vulnerable Employees
```{r}
   #plot
   p8 <- ggplot(data=p.dat_weekly.list[[8]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*21.797))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*21.797),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*7.407),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*7.407)),linetype=2)+ggtitle(label.list[8])+ylim(-27,10)
   p8
```

### Plot Log(GNI per capita)
```{r}
   p9 <- ggplot(data=p.dat_weekly.list[[9]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*10.747))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*10.747),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*9.242),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*9.242)),linetype=2)+ggtitle(label.list[9])+ylim(-27,10)
   p9
```

### Plot Health Expenditures
```{r}
   p10 <- ggplot(data=p.dat_weekly.list[[10]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*4292.73))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*4292.73),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*542.55),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*542.55)),linetype=2)+ggtitle(label.list[10])+ylim(-27,10)
   p10
```

### Plot Pollution
```{r}
   p11 <- ggplot(data=p.dat_weekly.list[[11]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*23.084))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*23.084),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*10.419),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*10.419)),linetype=2)+ggtitle(label.list[11])+ylim(-27,10)
   p11
```

### Plot EIU Democracy
```{r}
   p12 <- ggplot(data=p.dat_weekly.list[[12]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*8.207))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*8.207),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*6.570),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*6.570)),linetype=2)+ggtitle(label.list[12])+ylim(-27,10)
   p12
```

### Plot Trust
```{r}
   p13 <- ggplot(data=p.dat_weekly.list[[13]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.28083))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.28083),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*-0.13294),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*-0.13294)),linetype=2)+ggtitle(label.list[13])+ylim(-27,10)
   p13
```

### Plot Risk Taking
```{r}
   p14 <- ggplot(data=p.dat_weekly.list[[14]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.06918))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.06918),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*-0.15774),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*-0.15774)),linetype=2)+ggtitle(label.list[14])+ylim(-27,10)
   p14
```

### Arrange all plots
```{r}

p.all <- grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, ncol=4,nrow=3)
ggsave(file.path("Outputs_revision","Figure_heterogeneity_benchmark.png"), p.all, width = 12, height = 10)

```

### Baseline regressions - alternative SI (1)
```{r}

datweekly_panel <- datweekly_panel[order(datweekly_panel$Date),]
datweekly_panel <- datweekly_panel[order(datweekly_panel$COUNTRY),]
   
regmod <- list()
se_t_stats <- list()
se <- list()

###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
for (day_lead in seq(14,28,7)){
   
   datweekly_panel <- datweekly_panel %>%
      group_by(COUNTRY) %>%
      mutate(New_Mortality_Rate_Growth_lead_temp = dplyr::lead(New_Mortality_Rate_Growth,day_lead))
   
   datweekly_panel <- datweekly_panel %>% ungroup()
   datweekly_panel <- pdata.frame(datweekly_panel, index = c("COUNTRY", "Date"))
   datweekly_panel <- datweekly_panel[order(datweekly_panel$Date),]
   datweekly_panel <- datweekly_panel[order(datweekly_panel$COUNTRY),]

   regmod[[day_lead/7-1]] <- plm(lead(New_Mortality_Rate_Growth,day_lead)~SI_alt1+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead_temp)),],na.action="na.exclude")
   se[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))
   se_t_stats[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))[,2]
   
}
```

### HTML output of baseline regression results
```{r,warning=FALSE, results='hide',message=FALSE}
stargazer(digits=6,regmod,type="html",se=se_t_stats,out=file.path("Outputs_revision","Table_baseline_panel_output_SI_alt1.htm"),
          column.labels=c("Weekly New Mortality Growth (t+14)", "Weekly New Mortality Growth (t+21)", "Weekly New Mortality Growth (t+28)", "Weekly New Mortality Growth (t+35)"),
          covariate.labels=c("Stringency (t)","New Mortality Growth (t-1)"), df = FALSE,omit.stat="adj.rsq",notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",title="Local Projection Regressions",add.lines = list(c("Fixed effects?", "Y","Y","Y","Y")))
```

### Baseline regressions - alternative SI (2)
```{r}

datweekly_panel <- datweekly_panel[order(datweekly_panel$Date),]
datweekly_panel <- datweekly_panel[order(datweekly_panel$COUNTRY),]
   
regmod <- list()
se_t_stats <- list()
se <- list()

###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
for (day_lead in seq(14,28,7)){
   
   datweekly_panel <- datweekly_panel %>%
      group_by(COUNTRY) %>%
      mutate(New_Mortality_Rate_Growth_lead_temp = dplyr::lead(New_Mortality_Rate_Growth,day_lead))
   
   datweekly_panel <- datweekly_panel %>% ungroup()
   datweekly_panel <- pdata.frame(datweekly_panel, index = c("COUNTRY", "Date"))
   datweekly_panel <- datweekly_panel[order(datweekly_panel$Date),]
   datweekly_panel <- datweekly_panel[order(datweekly_panel$COUNTRY),]

   regmod[[day_lead/7-1]] <- plm(lead(New_Mortality_Rate_Growth,day_lead)~SI_alt2+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead_temp)),],na.action="na.exclude")
   se[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))
   se_t_stats[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))[,2]
   
}
```

### HTML output of baseline regression results
```{r,warning=FALSE, results='hide',message=FALSE}
stargazer(digits=6,regmod,type="html",se=se_t_stats,out=file.path("Outputs_revision","Table_baseline_panel_output_SI_alt2.htm"),
          column.labels=c("Weekly New Mortality Growth (t+14)", "Weekly New Mortality Growth (t+21)", "Weekly New Mortality Growth (t+28)", "Weekly New Mortality Growth (t+35)"),
          covariate.labels=c("Stringency (t)","New Mortality Growth (t-1)"), df = FALSE,omit.stat="adj.rsq",notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",title="Local Projection Regressions",add.lines = list(c("Fixed effects?", "Y","Y","Y","Y")))
```

### Baseline regressions - log(SI)
```{r}

datweekly_panel <- datweekly_panel[order(datweekly_panel$Date),]
datweekly_panel <- datweekly_panel[order(datweekly_panel$COUNTRY),]
# datweekly_panel <- datweekly_panel[which(datweekly_panel$StringencyIndex > 67),]

###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
regmoda<-plm(New_Mortality_Rate_Growth_lead14~log(StringencyIndex)+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
regmodb<-plm(New_Mortality_Rate_Growth_lead21~log(StringencyIndex)+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
regmodc<-plm(New_Mortality_Rate_Growth_lead28~log(StringencyIndex)+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
```

### HTML output of baseline regression results
```{r,warning=FALSE, results='hide',message=FALSE}
stargazer(digits=6,regmoda,regmodb,regmodc,type="html",se=list(se.a[,2],se.b[,2],se.c[,2]),out=file.path("Outputs_revision","Table_baseline_panel_output_logSI.htm"),
          dep.var.labels.include = FALSE,
          column.labels=c("Weekly New Mortality Growth (t+14)", "Weekly New Mortality Growth (t+21)", "Weekly New Mortality Growth (t+28)"),
          covariate.labels=c("Logged Stringency (t)","New Mortality Growth (t-1)"), df = FALSE,omit.stat="adj.rsq",notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",title="Local Projection Regressions",add.lines = list(c("Fixed effects?", "Y", "Y","Y")))
```

### Baseline regressions - Lagged SI
```{r}

datweekly_panel <- datweekly_panel[order(datweekly_panel$Date),]
datweekly_panel <- datweekly_panel[order(datweekly_panel$COUNTRY),]

###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
regmoda<-plm(New_Mortality_Rate_Growth_lead14~StringencyIndex+Lag(StringencyIndex,1)+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
regmodb<-plm(New_Mortality_Rate_Growth_lead21~StringencyIndex+Lag(StringencyIndex,1)+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
regmodc<-plm(New_Mortality_Rate_Growth_lead28~StringencyIndex+Lag(StringencyIndex,1)+New_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=datweekly_panel[which(!is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lag1) & !is.infinite(datweekly_panel$New_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
```

### HTML output of baseline regression results
```{r,warning=FALSE, results='hide',message=FALSE}
stargazer(digits=6,regmoda,regmodb,regmodc,type="html",se=list(se.a[,2],se.b[,2],se.c[,2]),out=file.path("Outputs_revision","Table_baseline_panel_output_laggedSI.htm"),
          dep.var.labels.include = FALSE,
          column.labels=c("Weekly New Mortality Growth (t+14)", "Weekly New Mortality Growth (t+21)", "Weekly New Mortality Growth (t+28)"),
          covariate.labels=c("Stringency (t)","Stringency (t-1)","New Mortality Growth (t-1)"), df = FALSE,omit.stat="adj.rsq",notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",title="Local Projection Regressions",add.lines = list(c("Fixed effects?", "Y", "Y","Y")))
```