
# Import library
```{r}
#getwd()
library(lubridate)
library(zoo)
library(quantmod)
library(fBasics)
library(tseries)
library(sandwich)
library(lmtest)
library(lattice)
library(xtable)
library(vars)
library(plyr)
library(gridExtra)
library(corrplot)
library(ggplot2)
library(reshape2)
library(data.table)
library(rvest)
library(plm)
library(tidyverse)
library(stringr)
library(stargazer)

```

### Read Final_Data_Country
```{r}
dat<-read.csv("./Data/Final_Data_Country.csv",header=T,sep=',')
# Remove factor variables for government responses and lagged variables
dat<-dat %>% select(-contains("Flag"))
dat<-dat %>% select(-contains("Lagged"))
dat$latitude <- NULL
dat$longitude <- NULL
```

### Merge global preference survey data to Final_Data_Country
```{r}
gps.country <- read.dta("./Data/GPS_dataset_country_level/country_v11.dta")
# Change country names for merge
gps.country[which(gps.country$country == "South Korea"),"country"] <- "Korea, South"
gps.country[which(gps.country$country == "Czech Republic"),"country"] <- "Czechia"
gps.country[which(gps.country$country == "United States"),"country"] <- "US"

gps.individual <- read.dta("./Data/GPS_dataset_individual_level/individual_v11_new.dta")
# Change country names for merge
gps.individual[which(gps.individual$country == "South Korea"),"country"] <- "Korea, South"
gps.individual[which(gps.individual$country == "Czech Republic"),"country"] <- "Czechia"
gps.individual[which(gps.individual$country == "United States"),"country"] <- "US"

gps.individual$age <- as.character(gps.individual$age)
gps.individual[which(gps.individual$age == "99 99+"), "age"] <- "99"
gps.individual[which(gps.individual$age == "100 (Refused"), "age"] <- NA
gps.individual$age <- as.numeric(gps.individual$age)
gps.individual.pop65 <- gps.individual[which(!is.na(gps.individual$age) & gps.individual$age > 65), ]
gps.individual.pop65 <- gps.individual.pop65[which(!is.na(gps.individual.pop65$trust)),]
gps.country.pop65 <- ddply(gps.individual.pop65, "country", function(X) data.frame(wm.trust = weighted.mean(X$trust, X$wgt)))

colnames(gps.country)[1] <- "COUNTRY"
dat <- merge(dat, gps.country, by=c("COUNTRY"), all.x=TRUE)
colnames(gps.country.pop65)[1] <- "COUNTRY"
dat <- merge(dat, gps.country.pop65, by=c("COUNTRY"), all.x=TRUE)
```

### Rename variables and create some new variables
```{r}
p.dat_cum <- pdata.frame(dat, index = c("COUNTRY", "Date"))
p.dat_cum$Date<-as.Date(p.dat_cum$Date,"%Y-%m-%d")
#reorder
p.dat_cum <- p.dat_cum[order(p.dat_cum$Date),]
p.dat_cum <- p.dat_cum[order(p.dat_cum$COUNTRY),]

colnames(p.dat_cum)[colnames(p.dat_cum) == "Total_Cases_Country"] <- "Total_Case_Country"
colnames(p.dat_cum)[colnames(p.dat_cum) == "Total_Deceased_Country"] <- "Total_Death_Country"
colnames(p.dat_cum)[colnames(p.dat_cum) == "New_Confirmed_Country"] <- "New_Case_Country"
colnames(p.dat_cum)[colnames(p.dat_cum) == "New_Total_Deceased_Country"] <- "New_Death_Country"
colnames(p.dat_cum)[colnames(p.dat_cum) == "Total_Mortality_Rate_Per_Capita"] <- "Total_Mortality_Rate"
colnames(p.dat_cum)[colnames(p.dat_cum) == "New_Mortality_Rate_Per_Capita"] <- "New_Mortality_Rate"
colnames(p.dat_cum)[colnames(p.dat_cum) == "Total_Cases_Country_Per_Capita"] <- "Total_Case_Rate"
colnames(p.dat_cum)[colnames(p.dat_cum) == "rolling_average_confirmed"] <- "RollingAverage_New_Case_Country"
colnames(p.dat_cum)[colnames(p.dat_cum) == "rolling_average_deceased"] <- "RollingAverage_New_Death_Country"
colnames(p.dat_cum)[colnames(p.dat_cum) == "total_rolling_average_mortality"] <- "RollingAverage_Total_Mortality_Rate"
colnames(p.dat_cum)[colnames(p.dat_cum) == "new_rolling_average_mortality"] <- "RollingAverage_New_Mortality_Rate"
colnames(p.dat_cum)[colnames(p.dat_cum) == "EUI_democracy"] <- "EIU_Democracy"
p.dat_cum$RollingAverage_Total_Mortality_Rate <- NULL
p.dat_cum$longitude <- NULL

p.dat_cum$New_Case_Rate = p.dat_cum$New_Case_Country/p.dat_cum$Population

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(RollingAverage_New_Case_Rate = frollmean(New_Case_Rate, 7,na.rm=TRUE))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(Total_Mortality_Rate_Growth = log(Total_Mortality_Rate) - Lag(log(Total_Mortality_Rate),7))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(Total_Case_Rate_Growth = log(Total_Case_Rate) - Lag(log(Total_Case_Rate),7))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(New_Case_Rate_Growth = log(RollingAverage_New_Case_Rate) - Lag(log(RollingAverage_New_Case_Rate),7))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(New_Mortality_Rate_Growth = log(RollingAverage_New_Mortality_Rate) - Lag(log(RollingAverage_New_Mortality_Rate),7))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(Total_Mortality_Rate_Growth_lag1 = dplyr::lag(Total_Mortality_Rate_Growth,1))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(Total_Mortality_Rate_Growth_lead7 = dplyr::lead(Total_Mortality_Rate_Growth,7))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(Total_Mortality_Rate_Growth_lead14 = dplyr::lead(Total_Mortality_Rate_Growth,14))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(Total_Mortality_Rate_Growth_lead21 = dplyr::lead(Total_Mortality_Rate_Growth,21))

p.dat_cum <- p.dat_cum %>%
  group_by(COUNTRY) %>%
  mutate(Total_Mortality_Rate_Growth_lead28 = dplyr::lead(Total_Mortality_Rate_Growth,28))

p.dat_cum$respiratory_deaths_rate <- 1/3*(p.dat_cum$respiratory_deaths/p.dat_cum$Population)
```

### Reorder columns
```{r}
p.dat_cum <- p.dat_cum %>%
 select(c("COUNTRY", "X", "Date",
          "Total_Case_Country", "Total_Death_Country", "New_Case_Country", "New_Death_Country", "Population",
          "Total_Case_Rate", "Total_Mortality_Rate", "New_Case_Rate", "New_Mortality_Rate", 
          "RollingAverage_New_Case_Country", "RollingAverage_New_Death_Country", 
          "RollingAverage_New_Case_Rate", "RollingAverage_New_Mortality_Rate", 
          "Total_Case_Rate_Growth", "Total_Mortality_Rate_Growth", 
          "New_Case_Rate_Growth", "New_Mortality_Rate_Growth"), everything())

p.dat_cum$Total_Case_Rate_Growth[is.nan(p.dat_cum$Total_Case_Rate_Growth)] <- NA
p.dat_cum$Total_Mortality_Rate_Growth[is.nan(p.dat_cum$Total_Mortality_Rate_Growth)] <- NA

p.dat_cum$New_Case_Rate_Growth[is.nan(p.dat_cum$New_Case_Rate_Growth)] <- NA
p.dat_cum$New_Mortality_Rate_Growth[is.nan(p.dat_cum$New_Mortality_Rate_Growth)] <- NA

p.dat_cum$New_Mortality_Rate_Growth[is.infinite(-p.dat_cum$New_Mortality_Rate_Growth)] <- Inf

colnames(p.dat_cum)
```

### Baseline regressions
```{r}
regmod <- list()
se_t_stats <- list()
se <- list()

###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
for (day_lead in seq(14,28,7)){
   p.dat_cum <- p.dat_cum %>%
      group_by(COUNTRY) %>%
      mutate(Total_Mortality_Rate_Growth_lead_temp = dplyr::lead(Total_Mortality_Rate_Growth,day_lead))
   
   p.dat_cum <- p.dat_cum %>% ungroup()
   p.dat_cum <- pdata.frame(p.dat_cum, index = c("COUNTRY", "Date"))
   p.dat_cum <- p.dat_cum[order(p.dat_cum$Date),]
   p.dat_cum <- p.dat_cum[order(p.dat_cum$COUNTRY),]
   
   regmod[[day_lead/7-1]] <- plm(lead(Total_Mortality_Rate_Growth,day_lead)~StringencyIndex+Total_Mortality_Rate_Growth_lag1,method="pooling",effect="twoways",data=p.dat_cum[which(!is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lag1) & !is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lead_temp)),],na.action="na.exclude")
   se[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))
   se_t_stats[[day_lead/7-1]] <- coeftest(regmod[[day_lead/7-1]], vcov = vcovHC(regmod[[day_lead/7-1]], type = "HC1", cluster="group"))[,2]
   
}
```


### HTML output of baseline regression results
```{r,warning=FALSE, results='hide',message=FALSE}
stargazer(digits=6,regmod,type="html",se=se_t_stats,out=file.path("Outputs_revision","Table_Appendix_baseline_panel_output.htm"),
          column.labels=c("Cum. Mortality Growth (t+14)", "Cum. Mortality Growth (t+21)", "Cum. Mortality Growth (t+28)"),
          dep.var.labels.include = FALSE,
          covariate.labels=c("Stringency (t)", "Cum. Mortality Growth (t-1)"), df = FALSE,omit.stat="adj.rsq",notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",title="Local Projection Regressions",add.lines = list(c("Fixed effects?", "Y", "Y","Y")))
```

### Plots
```{r}
### plot of 10-unit increase in Stringency effects over time on future mortality growth
p.dat_weekly<-c(coef(regmod[[1]])[1],coef(regmod[[2]])[1],coef(regmod[[3]])[1])
p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly+1.96*c(se[[1]][1,2],se[[2]][1,2],se[[3]][1,2]))
p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly[,1]-1.96*c(se[[1]][1,2],se[[2]][1,2],se[[3]][1,2]))
colnames(p.dat_weekly)<-c("mean","upper","lower")
p.dat_weekly<-data.frame(p.dat_weekly)*10*100
                                                                                   
p0<-ggplot(data=p.dat_weekly,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean))+geom_point(size=4,shape=21,fill="grey")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on New Mortality Growth (%)")+geom_errorbar(aes(ymin=lower,ymax=upper))+ggtitle("Average Impact")

ggsave(file.path("Outputs_revision","Figure_Appendix_baseline_panel.png"), width = 5, height = 5)
                                                                                                                
p0
```


### Loop to generate heterogeneity regression results
```{r}
###baseline projection regressions, remove 'infinite' values. two-way FE, HAC robust SEs, clustered on country
var.list <- c("prop65", "propurban", "Latitude", "Longitude", "popdensity", "arrivals", "departures", "vul_emp", "GNI", "health_exp", "pollution", "EIU_Democracy", "trust", "risktaking")
label.list <- c("Proportion 65+", "Proportion Urban", "Latitude", "Longitude", "Population Density", "Log(Arrivals)", "Log(Departures)", "Vulnerable Employees", "Log(GNI per capita)", "Health Expenditures", "Pollution", "EIU Democracy", "Trust", "Risk Taking")

p.dat_weekly.list <- list()
s.list <- list()

for (i in c(1:length(var.list))){

   var <- var.list[i]
   label <- label.list[i]
   
   if (var == "arrivals" || var == "departures" || var == "GNI"){
      regmoda<-plm(as.formula(paste("Total_Mortality_Rate_Growth_lead14~StringencyIndex","+Total_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")")),method="pooling",effect="twoways",data=p.dat_cum[which(!is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lag1) & !is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
      se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
      regmodb<-plm(as.formula(paste("Total_Mortality_Rate_Growth_lead21~StringencyIndex","+Total_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")")),method="pooling",effect="twoways",data=p.dat_cum[which(!is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lag1) & !is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
      se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
      regmodc<-plm(as.formula(paste("Total_Mortality_Rate_Growth_lead28~StringencyIndex","+Total_Mortality_Rate_Growth_lag1","+StringencyIndex:","log(",var,")")),method="pooling",effect="twoways",data=p.dat_cum[which(!is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lag1) & !is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
      se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
   }else{
   regmoda<-plm(as.formula(paste("Total_Mortality_Rate_Growth_lead14~StringencyIndex","+Total_Mortality_Rate_Growth_lag1","+StringencyIndex:",var)),method="pooling",effect="twoways",data=p.dat_cum[which(!is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lag1) & !is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lead14)),],na.action="na.exclude")
   se.a<-coeftest(regmoda, vcov = vcovHC(regmoda, type = "HC1", cluster="group"))
   regmodb<-plm(as.formula(paste("Total_Mortality_Rate_Growth_lead21~StringencyIndex","+Total_Mortality_Rate_Growth_lag1","+StringencyIndex:",var)),method="pooling",effect="twoways",data=p.dat_cum[which(!is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lag1) & !is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lead21)),],na.action="na.exclude")
   se.b<-coeftest(regmodb, vcov = vcovHC(regmodb, type = "HC1", cluster="group"))
   regmodc<-plm(as.formula(paste("Total_Mortality_Rate_Growth_lead28~StringencyIndex","+Total_Mortality_Rate_Growth_lag1","+StringencyIndex:",var)),method="pooling",effect="twoways",data=p.dat_cum[which(!is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lag1) & !is.infinite(p.dat_cum$Total_Mortality_Rate_Growth_lead28)),],na.action="na.exclude")
   se.c<-coeftest(regmodc, vcov = vcovHC(regmodc, type = "HC1", cluster="group"))
   }
   
   stargazer(digits=6,regmoda,regmodb,regmodc,type="html",
             se=list(se.a[,2],se.b[,2],se.c[,2]),out=paste("Table_Appendix_panel_",var,"_weekly_reg_output_benchmark.htm", sep = ""),
             dep.var.labels.include = FALSE,
             column.labels=c("Cum. Mortality Growth (t+14)", "Cum. Mortality Growth (t+21)", "Cum. Mortality Growth (t+28)"),
             covariate.labels=c("Stringency (t)","Cum. Mortality Growth (t-1)",paste("Stringency (t) X ", label)), 
             df = FALSE,omit.stat="adj.rsq",
             notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively.","HAC robust standard errors, clustered by country. Time and Country FEs."),notes.append=F,notes.align ="l",
             title=paste("Heterogeneity: ", label),add.lines = list(c("Fixed effects?", "Y","Y","Y")))
   
   ### plot of 10-unit increase in Stringency effects over time on future mortality growth
   p.dat<-c(coef(regmoda)[1],coef(regmodb)[1],coef(regmodc)[1])
   i.dat<-c(coef(regmoda)[3],coef(regmodb)[3],coef(regmodc)[3])
   effect.dat<-cbind(p.dat, i.dat)
   #p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly+1.96*c(se.a[2,2],se.b[2,2],se.c[2,2],se.d[2,2]))
   #p.dat_weekly<-cbind(p.dat_weekly,p.dat_weekly[,1]-1.96*c(se.a[2,2],se.b[2,2],se.c[2,2],se.d[2,2]))
   colnames(effect.dat)<-c("mean.1", "mean.2")
   
   p.dat.list[[i]]<-data.frame(effect.dat)*10*100
   
   ###figure out the 25% percentile  and 75% percentile of elderly population rate across countries, to compare effects of a 10-unit rise in stringency level
   if (var == "arrivals" || var == "departures" || var == "GNI"){
      
   s.list[[i]] <- summary(unique(log(p.dat_cum[[var]])))
   }else{
      s.list[[i]] <- summary(unique(p.dat_cum[[var]]))
   }
   s.list
}

```

### Plot Proportion 65+
```{r}
   #plot
   p1 <- ggplot(data=p.dat.list[[1]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*19.400))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*19.400),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+geom_point(size=4,aes(y=mean.1+mean.2*8.283),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*8.283)),linetype=2)+ggtitle(label.list[1])+ylim(-20,10)
   p1
   
```

### Plot Proportion Urban
```{r}
   #plot
   p2 <- ggplot(data=p.dat.list[[2]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*86.56))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*86.56),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*66.47),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*66.47)),linetype=2)+ggtitle(label.list[2])+ylim(-20,10)
   p2
```

### Plot Latitude
```{r}
   #plot
   p3 <- ggplot(data=p.dat.list[[3]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*50.83))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*50.83),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*22.01),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*22.01)),linetype=2)+ggtitle(label.list[3])+ylim(-20,10)
   p3
   
```

### Plot Longitude
```{r}
   #plot
   p4 <- ggplot(data=p.dat.list[[4]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*49.333))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*49.333),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*3.342),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*3.342)),linetype=2)+ggtitle(label.list[4])+ylim(-20,10)
   p4
```

### Plot Population Density
```{r}
   #plot
   p5 <- ggplot(data=p.dat.list[[5]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*223.847))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*223.847),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*33.375),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*33.375)),linetype=2)+ggtitle(label.list[5])+ylim(-20,10)
   p5
```

### Plot Log Arrivals
```{r}
   #plot
   p6 <- ggplot(data=p.dat.list[[6]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.94))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.94),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*15.30),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*15.30)),linetype=2)+ggtitle(label.list[6])+ylim(-20,10)
   p6
```

### Plot Log Departures
```{r}
   #plot
   p7 <- ggplot(data=p.dat.list[[7]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.79))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*16.79),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*15.02),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*15.02)),linetype=2)+ggtitle(label.list[7])+ylim(-20,10)
   p7
```

### Plot Vulnerable Employees
```{r}
   #plot
   p8 <- ggplot(data=p.dat.list[[8]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*21.797))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*21.797),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*7.407),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*7.407)),linetype=2)+ggtitle(label.list[8])+ylim(-20,10)
   p8
```

### Plot Log(GNI per capita)
```{r}
   p9 <- ggplot(data=p.dat.list[[9]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*10.747))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*10.747),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*9.242),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*9.242)),linetype=2)+ggtitle(label.list[9])+ylim(-20,10)
   p9
```

### Plot Health Expenditures
```{r}
   p10 <- ggplot(data=p.dat.list[[10]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*4292.73))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*4292.73),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*542.55),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*542.55)),linetype=2)+ggtitle(label.list[10])+ylim(-20,10)
   p10
```

### Plot Pollution
```{r}
   p11 <- ggplot(data=p.dat.list[[11]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*23.084))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*23.084),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*10.419),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*10.419)),linetype=2)+ggtitle(label.list[11])+ylim(-20,10)
   p11
```

### Plot EIU Democracy
```{r}
   p12 <- ggplot(data=p.dat.list[[12]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*8.207))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*8.207),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*6.570),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*6.570)),linetype=2)+ggtitle(label.list[12])+ylim(-20,10)
   p12
```

### Plot Trust
```{r}
   p13 <- ggplot(data=p.dat.list[[13]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.28083))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.28083),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*-0.13294),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*-0.13294)),linetype=2)+ggtitle(label.list[13])+ylim(-20,10)
   p13
```

### Plot Risk Taking
```{r}
   p14 <- ggplot(data=p.dat.list[[14]],aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.06918))+geom_line(group=1,aes(x=c("2 weeks","3 weeks","4 weeks"),y=mean.1+mean.2*0.06918),linetype=2)+geom_point(size=4,shape=22,fill="red")+geom_hline(yintercept=0,linetype=2)+xlab("")+theme_bw()+ylab("Effect on Cumulative Mortality Growth (%)")+
   geom_point(size=4,aes(y=mean.1+mean.2*-0.15774),shape=21,fill="blue")+geom_line(group=1,aes(y=c(mean.1+mean.2*-0.15774)),linetype=2)+ggtitle(label.list[14])+ylim(-20,10)
   p14
```

### Arrange all plots
```{r}

p.all <- grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, ncol=4,nrow=3)
ggsave(file.path("Outputs_revision","Figure_Appendix_heterogeneity.png"), p.all, width = 12, height = 10)

```

